A profile is a set of configuration settings.

Currently three profiles are supported. The default profile is profile {\ttfamily 0}.

\subsection*{Changing profiles}

Profiles can be selected using a G\+U\+I or the following stick combinations\+:

\begin{TabularC}{5}
\hline
\rowcolor{lightgray}{\bf Profile }&{\bf Throttle }&{\bf Yaw }&{\bf Pitch }&{\bf Roll  }\\\cline{1-5}
0 &Down &Left &Middle &Left \\\cline{1-5}
1 &Down &Left &Up &Middle \\\cline{1-5}
2 &Down &Left &Middle &Right \\\cline{1-5}
\end{TabularC}
The C\+L\+I {\ttfamily profile} command can also be used\+:

``` profile $<$index$>$ ```

\section*{Rate Profiles}

Cleanflight supports rate profiles in addition to regular profiles.

Rate profiles contain settings that adjust how your craft behaves based on control input.

Three rate profiles are supported.

Rate profiles can be selected while flying using the inflight adjustments feature.

Each normal profile has a setting called 'default\+\_\+rate\+\_\+profile`. When a profile is activated the corresponding rate profile is also activated.

Profile 0 has a default rate profile of 0. Profile 1 has a default rate profile of 1. Profile 2 has a default rate profile of 2.

The defaults are set this way so that it's simple to configure a profile and a rate profile at the same.

The current rate profile can be shown or set using the C\+L\+I {\ttfamily rateprofile} command\+:

``` rateprofile $<$index$>$ ```

The values contained within a rate profile can be seen by using the C\+L\+I {\ttfamily dump rates} command.

e.\+g ``` \section*{dump rates}

\section*{rateprofile}

rateprofile 0

set rc\+\_\+rate = 90 set rc\+\_\+expo = 65 set thr\+\_\+mid = 50 set thr\+\_\+expo = 0 set roll\+\_\+pitch\+\_\+rate = 0 set yaw\+\_\+rate = 0 set tpa\+\_\+rate = 0 set tpa\+\_\+breakpoint = 1500 ``` 