Building for Ubuntu platform is remarkably easy. The only trick to understand is that the Ubuntu toolchain, which they are downstreaming from Debian, is not compatible with Cleanflight. We suggest that you take an alternative P\+P\+A from Terry Guo, found here\+: \href{https://launchpad.net/~terry.guo/+archive/ubuntu/gcc-arm-embedded}{\tt https\+://launchpad.\+net/$\sim$terry.\+guo/+archive/ubuntu/gcc-\/arm-\/embedded}

This P\+P\+A has several compiler versions and platforms available. For many hardware platforms (notably Naze) the 4.\+9.\+3 compiler will work fine. For some, older compiler 4.\+8 (notably Sparky) is more appropriate. We suggest you build with 4.\+9.\+3 first, and try to see if you can connect to the C\+L\+I or run the Configurator. If you cannot, please see the section below for further hints on what you might do.

\subsection*{Setup G\+N\+U A\+R\+M Toolchain}

Note specifically the last paragraph of Terry's P\+P\+A documentation -- Ubuntu carries its own package for {\ttfamily gcc-\/arm-\/none-\/eabi}, so you'll have to remove it, and then pin the one from the P\+P\+A. For your release, you should first remove any older pacakges (from Debian or Ubuntu directly), introduce Terry's P\+P\+A, and update\+: ``` sudo apt-\/get remove binutils-\/arm-\/none-\/eabi gcc-\/arm-\/none-\/eabi sudo add-\/apt-\/repository ppa\+:terry.\+guo/gcc-\/arm-\/embedded sudo apt-\/get update ```

For Ubuntu 14.\+10 (current release, called Utopic Unicorn), you should pin\+: ``` sudo apt-\/get install gcc-\/arm-\/none-\/eabi=4.\+9.\+3.\+2014q4-\/0utopic12 ```

For Ubuntu 14.\+04 (an L\+T\+S as of Q1'2015, called Trusty Tahr), you should pin\+: ``` sudo apt-\/get install gcc-\/arm-\/none-\/eabi=4.\+9.\+3.\+2014q4-\/0trusty12 ```

For Ubuntu 12.\+04 (previous L\+T\+S, called Precise Penguin), you should pin\+: ``` sudo apt-\/get install gcc-\/arm-\/none-\/eabi=4.\+9.\+3.\+2014q4-\/0precise12 ```

\subsection*{Building on Ubuntu}

After the A\+R\+M toolchain from Terry is installed, you should be able to build from source. ``` cd src git clone \href{mailto:git@github.com}{\tt git@github.\+com}\+:cleanflight/cleanflight.\+git cd cleanflight make T\+A\+R\+G\+E\+T=N\+A\+Z\+E ```

You'll see a set of files being compiled, and finally linked, yielding both an E\+L\+F and then a H\+E\+X\+: ``` ... arm-\/none-\/eabi-\/size ./obj/main/cleanflight\+\_\+\+N\+A\+Z\+E.elf text data bss dec hex filename 97164 320 11080 108564 1a814 ./obj/main/cleanflight\+\_\+\+N\+A\+Z\+E.elf arm-\/none-\/eabi-\/objcopy -\/\+O ihex --set-\/start 0x8000000 obj/main/cleanflight\+\_\+\+N\+A\+Z\+E.\+elf obj/cleanflight\+\_\+\+N\+A\+Z\+E.\+hex \$ ls -\/la obj/cleanflight\+\_\+\+N\+A\+Z\+E.\+hex -\/rw-\/rw-\/r-- 1 pim pim 274258 Jan 12 21\+:45 obj/cleanflight\+\_\+\+N\+A\+Z\+E.\+hex ```

You can use the Cleanflight-\/\+Configurator to flash the {\ttfamily obj/cleanflight\+\_\+\+N\+A\+Z\+E.\+hex} file.

\subsection*{Bricked/\+Bad build?}

Users have reported that the 4.\+9.\+3 compiler for A\+R\+M produces bad builds, for example on the Sparky hardware platform. It is very likely that using an older compiler would be fine -- Terry happens to have also a 4.\+8 2014q2 build in his P\+P\+A -\/ to install this, you can fetch the {\ttfamily .deb} directly\+: \href{http://ppa.launchpad.net/terry.guo/gcc-arm-embedded/ubuntu/pool/main/g/gcc-arm-none-eabi/}{\tt http\+://ppa.\+launchpad.\+net/terry.\+guo/gcc-\/arm-\/embedded/ubuntu/pool/main/g/gcc-\/arm-\/none-\/eabi/}

and use {\ttfamily dpkg} to install\+: ``` sudo dpkg -\/i gcc-\/arm-\/none-\/eabi\+\_\+4-\/8-\/2014q2-\/0saucy9\+\_\+amd64.\+deb ```

Make sure to remove {\ttfamily obj/} and {\ttfamily make clean}, before building again.

\subsection*{Updating and rebuilding}

Navigate to the local cleanflight repository and use the following steps to pull the latest changes and rebuild your version of cleanflight\+:

``` cd src/cleanflight git reset --hard git pull make clean T\+A\+R\+G\+E\+T=N\+A\+Z\+E make ```

Credit goes to K.\+C. Budd, A\+Kfreak for testing, and pulsar for doing the long legwork that yielded this very short document. 